Supporting Information

### 2016-08-18 portfolio/text/supp.Rnw
Add draft captions to supplemental figures

\begin{equation}
\widehat{\log(R_{i,t})} = \beta_{0,j,t} +
  \beta_{1,j} S_{i,t} I_{i,t} +
  \beta_{2,j} S_{i,t} I_{i,t} +
  \beta_3 D_{i,t} +
  \beta_4 S_{i,t} D_{i,t} I_{i,t} +
  \beta_5 S_{i,t} D_{i,t} I_{i,t} +
  \log(R_{i,t-1})
\end{equation}

@@

\begin{equation}
\widehat{\sigma_{i,t}} =
\exp \left( \gamma_{0,j} + \eta_1 M_j +
\gamma_{1,j} S_{i,t} I_{i,t} +
\gamma_{2,j} S_{i,t} I_{i,t} +
\gamma_3 D_{i,t} +
\gamma_4 S_{i,t} D_{i,t} I_{i,t} +
\gamma_5 S_{i,t} D_{i,t} I_{i,t}\right),
\end{equation}

@@

\begin{table}[h!]
  \centering
  \caption{Caption.}
  \label{tab:strategies}
  \begin{tabular}{ll}
  \toprule
\input{../figs/strategy-table.tex}
  \end{tabular}
\end{table}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=5in]{../figs/stan-main-effects.pdf}
\caption{Caption here}
\label{fig:fe}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.05\textwidth]{../figs/stan-str-posteriors-dot.pdf}
\caption{Caption here}
\label{fig:re}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/stan-gg-spoke-all.pdf}
\caption{Caption here}
\label{fig:spoke-all}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/stan-offset-panel-mean-resid.png}
\caption{Caption here}
\label{fig:resid}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/stan-offset-panel-mean-resid-down.png}
\caption{Downside only}
\label{fig:resid-downside}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/strategy-year-effects.pdf}
\caption{Caption here}
\label{fig:str-yrs}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=0.7\textwidth]{../figs/lmer-vs-stan.pdf}
\caption{Caption here}
\label{fig:lmer-stan}
\end{center}
\end{figure}

>>>>

\begin{equation}
\label{eq:mean}
\widehat{\log(R_{i,t})} = \beta_{0,j,t} +
  \beta_{1,j} S_{i,t} I_{i,t} +
  \beta_{2,j} S_{i,t} I_{i,t} +
  \beta_3 D_{i,t} +
  \beta_4 S_{i,t} D_{i,t} I_{i,t} +
  \beta_5 S_{i,t} D_{i,t} I_{i,t} +
  \log(R_{i,t-1})
\end{equation}

@@

\begin{equation}
\label{eq:cv}
\widehat{\sigma_{i,t}} =
\exp \left( \gamma_{0,j} + \eta_1 M_j +
\gamma_{1,j} S_{i,t} I_{i,t} +
\gamma_{2,j} S_{i,t} I_{i,t} +
\gamma_3 D_{i,t} +
\gamma_4 S_{i,t} D_{i,t} I_{i,t} +
\gamma_5 S_{i,t} D_{i,t} I_{i,t}\right),
\end{equation}

@@

\begin{table}[h!]
  \centering
  \caption{Labels and descriptions of fishing strategies. In many cases, 
a particular strategy represents a group of similar permits across areas 
or vessel sizes. These strategies all had at least 100 
permit holders.}
  \label{tab:strategies}
  \begin{tabular}{ll}
  \toprule
\input{../figs/strategy-table.tex}
  \end{tabular}
\end{table}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=5in]{../figs/stan-main-effects.pdf}
\caption{Main effects from the hierarchical model 
predicting revenue (b or $\beta$) and variability (g or $\gamma$) in revenue.
The coefficient $u_1$ represents a strategy level predictor
relating mean species diversity of a strategy
to the expected magnitude of residual error.}
\label{fig:fe}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1.06\textwidth]{../figs/stan-str-posteriors-dot.pdf}
\caption{Estimates of within strategy effects from the hierarchical model. 
Panels refer in order to $\gamma_0$ (g0), $\gamma_1$ (g1), $\gamma_2$ (g2),
$\beta_1$ (b1), and $\beta_2$ (b2) from Eqns \ref{eq:mean} and \ref{eq:cv}.
Shown are medians (dots) and 50\% and 90\% credible intervals
(thick and thin line segments).
Strategies are ordered from high to low mean
species diversity from top to bottom.}
\label{fig:re}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/stan-gg-spoke-all.pdf}
\caption{The effect of adding a permit to ones strategy
on estimated revenue variability and median revenue.
This is an extended version of Fig.~2 that includes all major 
strategy combinations.}
\label{fig:spoke-all}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/stan-offset-panel-mean-resid.png}
\caption{The log-absolute value residuals from the mean-component model (Eq.~\ref{eq:mean}).
It is these residuals that are modeled in the variance-component model
(Eq.~\ref{eq:cv}).
Breakpoint linear regression fits are overlaid in red for visual interpretation.}
\label{fig:resid}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/stan-offset-panel-mean-resid-down.png}
\caption{The log-absolute value of downside (negative) residuals from the main
component model.
Figure looks qualitatively the same as Fig.~\ref{fig:resid} and so justifies
using variability (positive and negative residuals) as a measure of risk.}
\label{fig:resid-downside}
\end{center}
\end{figure}

\begin{figure}[htbp]
\begin{center}
\includegraphics[width=1\textwidth]{../figs/strategy-year-effects.pdf}
\caption{Strategy-year intercept estimates ($\beta_{0,j,t}$ in
Eq.~\ref{eq:mean}) from the hierarchical model. 
Shown are 40 samples from the posterior distribution.}
\label{fig:str-yrs}
\end{center}
\end{figure}

% \begin{figure}[htbp]
% \begin{center}
% \includegraphics[width=0.9\textwidth]{../figs/lmer-vs-stan2.pdf}
% \caption{Comparison of }
% \label{fig:lmer-stan}
% \end{center}
% \end{figure}
